The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-04 outputs/paper/paper.Rmd
result session draft finished

In this session, we are going to explore the results from data analysis. Let's take a look at figure\@ref(fig:fig6), which is the total result of immunization reports. This graph shows that how different immunization rate between healthcare and mother reports are among 2872 participants. 58.9 percentage of immunization was reported by mothers, approximately 1691 people, 26.0 percentage for healthcare, approximately 747 people and finally 15.1 percentage for non-immunization which is approximately 434 people. With this numbers in mind, we are going to analyze why this phenomena occurred in Thailand with two focuses; the gap between healthcare records and mother's reports and non-immunization rate.
First, let's take a look at figure\@ref(fig:fig2). From this graph, we can observe that there is not much difference in mother's reports between rural and urban areas. However, there is significant gap in healthcare records. Percentage of healthcare records for urban is 41.5% and for rural is 22.8%. Following that, non immunization rate in rural areas is 17.2% which is more than 3 times of non immunization rate in urban, 5.3%. This two gaps indicate that there needs more healthcare facilitates. In addition to that, percentage of mother's reports in rural areas is not 
low. This shows that there existed accessibility to vaccines in rural areas. Thus, we also conclude that lack of trust toward healthcare system could potentially affect the gap as well.

Second, from figure\@ref(fig:fig3), regional based immunization rate seems very similar trends with communities. All over the regions, there are more mother's reports than healthcare records. For some specific region such as South, Northeast and Central, the gap is wider than the other two.

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

>>>>

In this session, we are going to explore the results from data analysis. Let's take a look at figure\@ref(fig:fig6), which is the total result of immunization reports. This graph shows that how different immunization rate between healthcare and mother reports are among 2872 participants. 58.9 percentage of immunization was reported by mothers, approximately 1691 people, 26.0 percentage for healthcare, approximately 747 people and finally 15.1 percentage for non-immunization which is approximately 434 people. With this numbers in mind, we are going to analyze why this phenomena occurred in Thailand with two focuses; the gap between healthcare records and mother's reports and non-immunization rate

First, let's take a look at figure\@ref(fig:fig2). From this graph, we can observe that there is not much difference in mother's reports between rural and urban areas. However, there is significant gap in healthcare records. Percentage of healthcare records for urban is 41.5% and for rural is 22.8%. Following that, non immunization rate in rural areas is 17.2% which is more than 3 times of non immunization rate in urban, 5.3%. This two gaps indicate that there needs more healthcare facilitates. In addition to that, percentage of mother's reports in rural areas is not 
low. This shows that there existed accessibility to vaccines in rural areas. Thus, we also conclude that lack of trust toward healthcare system could potentially affect the gap as well.

Second, from figure\@ref(fig:fig3), regional based immunization rate shows very similar trends with that of communities. All over the regions, there are more mother's reports than healthcare records. For some specific region such as South, Northeast and Central, the gap is wider than the other two. Even there were more participants who answered non-immunization than health reports in south. One thing to notice from this graph is North part. Northern Thailand shows very similar trend with Bangkok unlike other regions. We suspect the existence of city, Chiang Mai for the unexpected result. Chiang Mai is a city with historical monument and you can enjoy beautiful landscape there. Following that, many tourists have been visiting the city. Therefore, there are more accessibility to healthcare facilities than that of other cities. Contrast to Chiang Mai, northeastern Thailand is more local. Extreme gap between mother reports and health record indirectly shows that there is short of the accessibility.

Third, figure\@ref(fig:fig4) presents an interesting result. While mother's reports with different education are similar, as education level goes up from no education to higher, healthcare records increase. Also, non-immunization rate decreases as it goes up. Non-immunization rate in higher education group is only 0.6%, on the other hand, it is 29.4% for no education group. If healthcare facilities were available to all, this scheme would not exist.

Lastly, figure\@ref(fig:fig5) represents immunization status along with religion. It shows that Buddhist got more immunization compared to that of Islam as well as healthcare records. Although Buddhist got more immunization, still its rate is mainly from mother's reports. One thing to notice here is that Islam in Thailand had non-immunization rate comparatively high. Like many variables above, we can suspect that there would be less accessibility to healthcare system in the Islamic communities.

# Discussion
In this s

## What can we learn about 1987 Thailand healthcare system?

## From results of analysis what should be enhanced?

## Weaknesses

## Next steps for future
